A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-05 tex/codatadp.tex
more

We presented a decision procedure for datatypes and codatatypes and implemented
it in the SMT solver CVC4. Our main theoretical contribution has been the
extension of the procedure with codatatypes. Codatatypes are not very difficult
per se, but there are tricky corner cases to take care of if we care about
completeness (which we do). On the practical side, we obtained interesting
results on Isabelle benchmarks, including some rather
%mind-boggling
puzzling bisimulation proofs.

@@

\def\ackname{Acknowledgment}
\paragraph{\ackname.}
We owe a great debt to Clark Barrett and Cesare Tinelli for datatype case blah
blah blah.
%
Our present and former bosses, Viktor Kuncak, Stephan Merz, Tobias Nipkow,
Cesare Tinelli, and Christoph Weidenbach, have either encouraged the research on
codatatype or at least tolerated it, both of which we are thankful for.
%
Blanchette's research was partially supported by the Deutsche
Forschungs\-gemein\-schaft (DFG) project
\relax{Hardening the Hammer} (grant Ni\,491\slash 14-1).

>>>>

We introduced a decision procedure for datatypes and codatatypes and implemented
it in the SMT solver CVC4. Our main theoretical contribution has been the
addition of codatatypes. These are not very difficult
per se, but there are tricky corner cases to take care of if we care about
completeness (which we do). On the practical side, we obtained interesting
results on benchmarks generated from Isabelle theories, including some rather
%mind-boggling
puzzling bisimulation proofs.

@@

\def\ackname{Acknowledgment}
\paragraph{\ackname.}
We owe a great debt to Clark Barrett and Cesare Tinelli for datatype case blah
blah blah.
%
Our present and former bosses, Viktor Kuncak, Stephan Merz, Tobias Nipkow,
Cesare Tinelli, and Christoph Weidenbach, have either encouraged the research on
codatatype or at least tolerated it, both of which we are thankful for.
%
Andreas Lochbihler and Peter Gammie shared their private codatatype-based
theories with us so we could include them in the benchmarks.
%
Blanchette's research was partially supported by the Deutsche
Forschungs\-gemein\-schaft (DFG) project
\relax{Hardening the Hammer} (grant Ni\,491\slash 14-1).
